\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\usepackage{assignment}
\settitle{Weekly Report 1}
\setauthor{Wanzhang Sheng}
\setcourse{Master Project}

\begin{document}

\maketitle % Print the title

\section{Project Information} % (fold)
\label{sec:project_information}
We will use D3 to visualize data gathered from SonicWall Firewall or similar data presented by sponsors, and complement what is already in Sonic Wall Scrutinizer and Analyzer. We should learn and implement basic UI design principles,and focus on presenting informative visualization to keep users.
% section project_information (end)

\section{Time Commitment} % (fold)
\label{sec:time_commitment}
For every one, we have a 30min(at most) meeting every weekday to keep agile on developing the design.
Since we have meeting with Sophie every Wednesday, that will be counted as the meeting for that day.
And we will work on the project in the afternoon after the meeting, from 1pm to 6pm.
In addition the class time we have 10.5 hours team time per week to share.
% section time_commitment (end)

\section{Team Roles} % (fold)
\label{sec:team_roles}
Our team will divide tasks to each indivituals based on the kind of the tasks.
Wanzhang Sheng will be the team leader to hold meeting.
Michelle Gao will scribe for meetings.
Kaiming Yang will review documentations.
All the people will be a owner of a part of the project's code.
The details will base on the detailed project specification and meeting result.
% section team_roles (end)

\section{Team Approach} % (fold)
\label{sec:team_approach}
On the daily meeting, we will discuss what we have done and the problem we met, and try to solve the critical hazard together.  A vote will be hold to make the decision if it's hard to reach agreement,. If vote still fails, the person who are responsible to (or willing to solve) the problem will make the decision.
% section team_approach (end)

\end{document}
